### 2015-02-02 paper_10_intro.tex
more typos fixed

    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithms to review past performance of estimates and modify the
    algorithm accordingly.  COCOMO II can be a useful tool for 
    estimating the time and costs within an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  Does that mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  Not matter the interpretation,
    the goal is to release the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

@@

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    properly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this work will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.

>>>>

    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithm to review and modify past performance 
    based upon estimates.  COCOMO II can be a useful tool for 
    estimating the time and costs within an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  Does that mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  No matter the interpretation,
    the goal is to release the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

@@

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    properly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    Some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this work will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.
